Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Add gas table

@@

\section{Evaluation} \label{evaluation}

@@

We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in the following table:

\begin{tabular}{l|l|l|l}
	% TODO
	a & b & c & d
\end{tabular}

Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{gas limit}, the maximum amount of gas that can be spent per transaction.
Even if that is not the case, a high gas cost is still a problem, since transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO explain?

@@

%Time for one instance
%Setup difficulty

>>>>

% tablespacing
\renewcommand{\arraystretch}{1.5}
\setlength\tabcolsep{0.2cm}

@@

\section{Discussion} \label{evaluation}

@@

We measured the gas used for each transaction that is executed by the Armadillo tool, and we summed up the gas usage for the different kinds of contracts in the companies in Table \ref{gasusage}:

\begin{table}
	\centering
	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
	\begin{tabular}{|l | c | c | c|}
		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
	\end{tabular}
\end{table}

Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block.
%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO why again?

@@
